Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
more text
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58594 72bbbca6-d526-0410-a7d9-f06f51895060
update text
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58595 72bbbca6-d526-0410-a7d9-f06f51895060

@@

The idea behind this was that the \emph{normalised} part of the corpus would be

@@

The idea of the end-to-end translation experiment was to evaluate how well the different 
normalisation strategies worked in combination with another language technology tool. To
evaluate this, we took the test corpus and translated it to English.

>>>>

The rules included both simple one-to-one (`m\"{a}' $\rightarrow$ `min\"{a}') and one-to-many (`emm\"{a}' $\rightarrow$ `en min\"{a}') word correspondences,
and also regular expression substitutions which could match a prefix or a suffix (`(?+)nkaa' $\rightarrow$ `\textbackslash1n kanssa').

@@

The idea behind this was that the \emph{normalised} part of the corpus would be closer
to the original colloquial text than the \emph{standardised} part, making it easier
to learn the alignment model.

@@

In order to evaluate how well the different normalisation strategies worked in 
combination with another language technology tool, we performed an end-to-end experiment
involving machine translation.
To evaluate this, we took the test corpus and translated it to English.
